
\newpage


\chapter{Epilog der Pod Programme}

\section{Inhalt}
Folgender Dialog erscheint am Ende von \dq Ende E \dq .  Er stellt die Beziehung von 9S zu 2B dar. 	\\
 Der Text ist identisch mit der Version im Spiel. Er wurde hier nur abgedruckt, da er nicht als bekannt vorausgesetzt wird. 


\section{Farmwell}
\subsection{Narration}

\begin{play}
	\speaker{\textbf{Pod 153}} \shortdirection{narration} Everything that lives is designed to end.
	\speaker{\textbf{Pod 153}} \shortdirection{narration} "We" are perpetually trapped ..
	\speaker{\textbf{Pod 153}} \shortdirection{narration} ... in a never-ending spiral of life and death.
	\speaker{\textbf{Pod 153}} \shortdirection{narration} Is this a curse?
	\speaker{\textbf{Pod 153}} \shortdirection{narration} Or some kind of punishment?
	\speaker{\textbf{Pod 153}} \shortdirection{narration}  I often think about the god who blessed us with this cryptic puzzle ...
	\speaker{\textbf{Pod 153}} \shortdirection{narration} ... and wonder if "we'll" ever have the chance to kill him.
\end{play}

\subsection{5. September 11945}

\begin{play}


\speaker{\textbf{Pod 042}}  Unit 2B's vital signs confirmed.

\speaker{\textbf{Pod 042}}  Memory storage, thought circuits, auxiliary motor functions, all confirmed to have been restarted.

\speaker{\textbf{Pod 042}}  Entering reboot sequence.

\speaker{\textbf{2B}}  Ugh ...

\speaker{\textbf{Pod 042}}  Good morning, 2B.

\speaker{\textbf{2B}}  I ...

\speaker{\textbf{Pod 042}}  Report: Unit 2B was killed by unit A2 approximately 1718 hours ago.

\speaker{\textbf{2B}}  1718 hours ago ... So ... 72 days, then.

\speaker{\textbf{Pod 042}}  Following that, us tactical support units reconstructed your parts.

\speaker{\textbf{Pod 042}}  The virus previously inside you deactivated along with the tower's collapse, and remains in suspension. 

\speaker{\textbf{2B}}  Tower ...? What happened ...?

(2B suddenly realizes something.)

\speaker{\textbf{2B}}  Ah!! 9S ...!!

\speaker{\textbf{Pod 153}}  Report: Unit 9S ceased activity approximately 740 hours ago.

\speaker{\textbf{2B}}  Pod ... 153?

\speaker{\textbf{Pod 153}}  Unit 9S was severely contaminated, however said virus deactivated along with the tower's collapse, and remains in suspension.

\speaker{\textbf{2B}}  So he's just ... asleep?

\speaker{\textbf{Pod 153}}  Negative: An error occurred during unit 9S's reboot sequence.

\speaker{\textbf{2B}}  What do you mean, an error ...?

\speaker{\textbf{Pod 153}} \shortdirection{narration} Unknown: All checks were completed, however his personal data will not begin loading procedures, causing an inability to reboot.

\speaker{\textbf{2B}}  His personal data won't load ... Then in that case, run the monitoring sequence, and skip the check sequence ...

\speaker{\textbf{Pod 153}} \shortdirection{narration} Negative: This unit has already attempted 345 combinations 34,500 times, and all have ended in failure.

\speaker{\textbf{Pod 153}} \shortdirection{narration} Unit 9S's current state suggests there is a possibility his personal data has been lost due to some unknown cause.

\speaker{\textbf{2B}}  His personal data is ... lost ...?

\speaker{\textbf{Pod 153}} \shortdirection{narration} Proposal: Unit 2B should consider disposing of unit 9S's body.

(2B speaks in a strong tone.)

\speaker{\textbf{2B}}  There's no way I could ... just dispose of his body ...!

(There is a considerable pause.)

\speaker{\textbf{Pod 153}} \shortdirection{narration} ... Understood.

\speaker{\textbf{2B}} \shortdirection{narration} After being reconstructed, there wasn't even a hint of dirt on 9S's body ...

\speaker{\textbf{2B}} \shortdirection{narration} His face ... looked just like he was sleeping.

\speaker{\textbf{2B}} \shortdirection{narration} I took my weapon in hand, and packed the minimum necessary provisions, before standing up.

\speaker{\textbf{2B}} \shortdirection{narration} I had to go.

\speaker{\textbf{2B}} \shortdirection{narration} There had to be a way to get 9S to reboot properly.

\speaker{\textbf{2B}} \shortdirection{narration} That's what I believed.
\end{play}


\subsection{14. September 11945}
\begin{play}
\speaker{\textbf{2B}} \shortdirection{narration} I received information on what happened while I was gone from the pods.

\speaker{\textbf{2B}} \shortdirection{narration} About A2 ... and 9S.

\speaker{\textbf{2B}} \shortdirection{narration} I also heard about how the two of them destroyed some huge "Tower" that had been created by the machine lifeforms.

\speaker{\textbf{2B}} \shortdirection{narration} The rubble from it is still scattered all throughout the city.

\speaker{\textbf{2B}} \shortdirection{narration} The City Ruins' landscape had been completely changed.

\speaker{\textbf{Pod 042}} \shortdirection{Proposal} Unit 2B should gather information at the resistance camp.

\speaker{\textbf{2B}} \shortdirection{narration} The resistance camp was able to miraculously avoid damage from the collapse of the tower ...

\speaker{\textbf{2B}} \shortdirection{narration} However Devola and Popola, and a few others in the resistance, lost their lives in the fight with the machines.

\speaker{\textbf{2B}} \shortdirection{narration} Even though Anemone was faced with such a difficult situation, she still remained level-headed.

\speaker{\textbf{2B}} \shortdirection{narration} I tried speaking to Anemone about the situation with 9S's rebooting, but she wasn't able to provide me with any helpful information.

\speaker{\textbf{Pod 042}} \shortdirection{Report} Relevant records within the Bunker have been lost.

\speaker{\textbf{2B}} \shortdirection{narration} We YoRHa units are a special type.

\speaker{\textbf{2B}} \shortdirection{narration} We contain something other androids don't within us — a Black Box.

\speaker{\textbf{2B}} \shortdirection{narration} And due to that, we're capable of much higher functionality. 

\speaker{\textbf{2B}} \shortdirection{narration} However, unlike general androids, our maintenance is only able to be done on the Bunker.

\speaker{\textbf{2B}} \shortdirection{narration} It's possible to make easy repairs with the small amount of materials and programs at access points, but detailed information about the insides of our bodies was lost along with the fall of the Bunker.

\speaker{\textbf{2B}} \shortdirection{narration} Even so, I was traveling from place to place looking for the information I needed.

\speaker{\textbf{2B}} \shortdirection{narration} No matter ... how long it took.

\speaker{\textbf{Pod 042}} \shortdirection{Alert} Unit 2B is taking damage due to maintenance failure.

\speaker{\textbf{Pod 042}} \shortdirection{Proposal} Unit 2B should perform proper repair and replenish materials.

\speaker{\textbf{2B}} \shortdirection{narration} With how tired I was, even doing simple first aid felt troublesome.

\speaker{\textbf{2B}} \shortdirection{narration} In the depths of my heart, I started to feel like ... everything I was doing was meaningless.

\speaker{\textbf{2B}} \shortdirection{narration} I don't ... care anymore.

\speaker{\textbf{2B}} \shortdirection{narration} I wonder if ... 9S will ever wake up.

\speaker{\textbf{2B}} \shortdirection{narration} That sort of dark thought process began to take over.

\speaker{\textbf{2B}} \shortdirection{narration} And I shook my head.

\speaker{\textbf{2B}} \shortdirection{narration} I couldn't give up. I couldn't give up. I couldn't give up.

\speaker{\textbf{2B}} \shortdirection{narration} Even if I was just deceiving myself, I couldn't admit that.

\speaker{\textbf{2B}} \shortdirection{narration} It caused my body to become heavy.

\speaker{\textbf{2B}} \shortdirection{narration} If I go further away from here, I may be able to find surviving YoRHa members.

\speaker{\textbf{Pod 042}} \shortdirection{Report} Mail notification received.

\speaker{\textbf{2B}}  ... Check it.

(The pod reads out the mail's contents in its usual tone of voice.)

\speaker{\textbf{Pod 153}}  Sender: Jackass.

\speaker{\textbf{Pod 153}}  Subject: About 9S's Personal Data Reboot.

\speaker{\textbf{Pod 153}}  Yo, how's it going, 2B?

\speaker{\textbf{Pod 153}}  I know a little something about 9S's condition.

\speaker{\textbf{Pod 153}}  I've been looking into a lot of things since everything happened, and I came across some concerning information.

\speaker{\textbf{Pod 153}}  There were some logs remaining in the access port outside of 9S's memory storage.

\speaker{\textbf{Pod 153}}  They were a communication record from the "Ark" object those machine lifeforms made.

\speaker{\textbf{Pod 153}}  I don't know anything about that "Ark" thing, but it might be some sort of server.

\speaker{\textbf{Pod 153}}  I'll send you the time and coordinates that were written in that log right away.

\speaker{\textbf{Pod 153}}  There might be a hint somewhere in them.

(There's a short pause.)

\speaker{\textbf{Pod 153}}  This concludes the body of the email. Time and three-dimensional coordinate data is attached.

\speaker{\textbf{2B}} \shortdirection{narration} Those coordinates ... were right in the area where the Tower collapsed.
	
	
	
\end{play}
\subsection{17. September 11945}
\begin{play}
\speaker{\textbf{2B}} \shortdirection{narration} Mountains and mountains of white rubble, as far as I could see.

\speaker{\textbf{2B}} \shortdirection{narration} I'd arrived at the center of where the Tower collapsed.

\speaker{\textbf{2B}} \shortdirection{narration} And it was there, where I began digging.

\speaker{\textbf{Pod 153}} \shortdirection{Hypothesis} Origin point is 40 meters below the current point.

\speaker{\textbf{Pod 042}} \shortdirection{Proposal} Proposal: Search for a more efficient method for digging.

\speaker{\textbf{2B}} \shortdirection{narration} That's right, the coordinates Jackass sent me pointed right to a location within the Tower's rubble.

\speaker{\textbf{2B}} \shortdirection{narration} I was digging through it so I could reach the position she gave me.

\speaker{\textbf{2B}} \shortdirection{narration} But the material was much more firm than I expected it to be, and my digging wasn't going particularly well.

\speaker{\textbf{2B}} \shortdirection{narration} My breath began to show, and before I'd realized it, it was snowing.

\speaker{\textbf{2B}} \shortdirection{narration} It seems the Tower's rubble was absorbing the surrounding area's heat and causing the area to cool.

\speaker{\textbf{2B}} \shortdirection{narration} According to the pods, it was made of materials derived from the bodies of machine lifeforms, which centered around silicon, among other things.

\speaker{\textbf{2B}} \shortdirection{narration} But that didn't matter.

\speaker{\textbf{2B}} \shortdirection{narration} I only cared about my digging.

\speaker{\textbf{Pod 153}} \shortdirection{Hypothesis} Origin point is 25 meters below the current point.

\speaker{\textbf{Pod 042}} \shortdirection{Proposal} Alert: Unit 2B is taking damage due to maintenance failure.

\speaker{\textbf{2B}} \shortdirection{narration} The Tower's materials became increasingly firm the further down I went.

\speaker{\textbf{2B}} \shortdirection{narration} I was using my weapon to dig, but I had to stop using my one-handed sword to switch to something better suited, and I proceeded downward by practically crushing the materials.

\speaker{\textbf{2B}} \shortdirection{narration} I continued on, my mind devoid of any other thoughts, until I finished.

\speaker{\textbf{2B}} \shortdirection{narration} I could feel an ache run through my pain sensors.

\speaker{\textbf{2B}} \shortdirection{narration} But it was only thanks to that pain that I was able to keep my sanity.

\speaker{\textbf{Pod 153}} \shortdirection{Hypothesis} Origin point is 12 meters below the current point.

\speaker{\textbf{Pod 042}} \shortdirection{Proposal} Alert: Unit 2B is taking damage due to maintenance failure.

\speaker{\textbf{Pod 042}} \shortdirection{Proposal} Alert: If no proper repair is performed, it will cause severe impact to the unit's body.

\speaker{\textbf{2B}} \shortdirection{narration} As I continued to dig, I found out what that "Ark" really was.

\speaker{\textbf{2B}} \shortdirection{narration} It seemed to be a huge memory unit, made by combining complex crystals.

\speaker{\textbf{2B}} \shortdirection{narration} However, as it'd been shattered to pieces, I couldn't find a single "living" crystal.

\speaker{\textbf{2B}} \shortdirection{narration} Regardless, I continued digging in search of the Ark's crystals.

\speaker{\textbf{2B}} \shortdirection{narration} With each swing of my weapon, blood began to scatter.

\speaker{\textbf{2B}} \shortdirection{narration} I couldn't feel my fingertips anymore, and the sensors running from my wrists had died.

\speaker{\textbf{2B}} \shortdirection{narration} The bolts I'd used to forcibly fix it were starting to dig into my skin.

\speaker{\textbf{2B}} \shortdirection{narration} But that didn't matter.

\speaker{\textbf{2B}} \shortdirection{narration} Somewhere up ahead, the information I needed to save 9S was ...

\speaker{\textbf{2B}} \shortdirection{narration} Even if only a little remains of the Ark, I ... I have to ...!!

(An error sound pings.)

\speaker{\textbf{Pod 042}} \shortdirection{Proposal} Alert: Unit 2B entered forced shutdown due to overload.
\end{play}
\subsection{19. September 11945}
\begin{play}
	\speaker{\textbf{Pod 042}}  Emergency nanomachine removal complete.
	
	\speaker{\textbf{Pod 042}}  Unit 2B's vital signs confirmed.
	
	\speaker{\textbf{Pod 042}}  Entering reboot sequence.
	
	(A long "beeeeep" alert sounds.)
	
	(Afterwards, a short three "beeps" sound.)
	
	\speaker{\textbf{Pod 042}}  Good morning, 2B.
	
	\speaker{\textbf{2B}}  Huh? I ...
	
	\speaker{\textbf{Pod 042}}  You entered a forced shutdown due to severe continuous operation.
	
	\speaker{\textbf{2B}} \shortdirection{narration} When I hurriedly asked about the Ark, the pods showed me a small, orange sparkling crystal.
	
	\speaker{\textbf{2B}} \shortdirection{narration} What they found seemed to be a remnant of the machine lifeforms' communication protocol.
	
	\speaker{\textbf{2B}} \shortdirection{narration} If we use that protocol and its data, we could create a key, and open up 9S's memory storage.
	
	\speaker{\textbf{2B}} \shortdirection{narration} Although I didn't understand the details, there was meaning in my continued digging.
	
	\speaker{\textbf{2B}} \shortdirection{narration} The pods siphoned out the data and recombined it to create a repair vaccine.
	
	\speaker{\textbf{2B}} \shortdirection{narration} Then, we could pull the cable from 9S's access port and create a wired connection.
	
	\speaker{\textbf{2B}} \shortdirection{narration} With that, I'd be able to insert the repair vaccine.
	
	\speaker{\textbf{2B}} \shortdirection{narration} After that, all I'd have to do is hope that 9S's memory storage data could be evacuated into his personal data.
	
	\speaker{\textbf{Pod 153}}  Repair vaccine injected.
	
	(Three seconds later, the sound of a heartbeat stops and a flatline beeps.)
	
	\speaker{\textbf{Pod 153}}  No effect. Re-administering repair vaccine.
	
	(Three seconds later, the sound of a heartbeat stops and a flatline beeps.)
	
	\speaker{\textbf{Pod 153}}  No effect. Re-administering repair vaccine.
	
	(Three seconds later, the sound of a heartbeat stops and a flatline beeps.)
	
	\speaker{\textbf{Pod 153}}  No effect.
	
	\speaker{\textbf{2B}}  Why ... Why isn't it ...?!
	
	\speaker{\textbf{Pod 042}} \shortdirection{Hypothesis} Repair vaccine is a failure.
	
	\speaker{\textbf{Pod 153}} \shortdirection{Negative} Repair vaccine's functions confirmed to be normal.
	
	\speaker{\textbf{2B}}  Try it again ... Administer it to him again!
	
	(Three seconds later, the sound of a heartbeat stops and a flatline beeps.)
	
	\speaker{\textbf{Pod 153}}  No effect.
	
	\speaker{\textbf{2B}}  Try ... again ...
	
	\speaker{\textbf{Pod 153}} \shortdirection{Report} Traces detected indicating the memory region of unit 9S's contents have been erased.
	
	\speaker{\textbf{Pod 042}} \shortdirection{Negative} It is an effect of the repair vaccine.
	
	\speaker{\textbf{Pod 042}} \shortdirection{Hypothesis} Unit 9S's personal data has been lost.
	
	\speaker{\textbf{2B}}  His personal data ... is lost ...?
	
	\speaker{\textbf{Pod 042}}  His personal data was wiped of his own accord, but there is the possibility it was moved to a different location.
	
	\speaker{\textbf{Pod 042}}  According to unit A2's records, it is possible his data evacuated using the machine lifeforms' Ark.
	
	\speaker{\textbf{Pod 042}} \shortdirection{Report} Possibility of recovering 9S's personal data extremely low.
	
	S.P.
	
	\speaker{\textbf{2B}}  No ...
	
	(Three beeps suddenly sound.)
	
	\speaker{\textbf{Pod 153}} \shortdirection{Report} Memory components discovered within traces of personal data.
	
	\speaker{\textbf{Pod 153}}  Partial playback possible of memory containing the reason behind his personal data's reparation failure.
	
	\speaker{\textbf{Pod 153}} \shortdirection{Query} Does unit 2B feel it necessary to repair this memory component?
	
	\speaker{\textbf{2B}}  ... Repair it.
	
	\speaker{\textbf{Pod 153}}  Understood.
	
	\speaker{\textbf{Pod 153}}  Data repair complete.
	
	\speaker{\textbf{Pod 153}}  Starting playback.
	
	(9S's voice begins to play back with the sound quality of a radio.)
	
	(He seems to be suffering.)
	
	\speaker{\textbf{9S}}  I didn't ... get on the Ark created by the machine lifeforms.
	
	\speaker{\textbf{9S}}  We YoRHa ... We don't deserve to be loved by this world ... We're just soldiers created to die ...
	
	\speaker{\textbf{9S}}  But I ... I think I'm glad ... that I was born as myself ...
	
	\speaker{\textbf{9S}}  My personal data, it ... it can't keep it's shape any longer.
	
	\speaker{\textbf{9S}}  I wonder if I'm about to disappear ...
	
	\speaker{\textbf{9S}}  But ... I'm okay with that ...
	
	(2B begins crying, without making a sound.)
	
	\speaker{\textbf{9S}}  Hey, 2B ... We're ... we're not immortal or anything.
	
	\speaker{\textbf{9S}}  Someday, we'll break down and return to the Earth.
	
	\speaker{\textbf{9S}}  But, my existence ... It wasn't meaningless ...
	
	\speaker{\textbf{9S}}  Meeting you ... gave meaning to my birth ...
	
	\speaker{\textbf{9S}}  Thank you ...
	
	\speaker{\textbf{9S}}  Thank you ...
	
	(9S's voice becomes hidden behind static.)
	
	(2B begins weeping.)
	
	\speaker{\textbf{2B}}  Nines ...
	
	\speaker{\textbf{Pod 042}} \shortdirection{narration} 2B didn't move from where she was.
	
	\speaker{\textbf{Pod 042}} \shortdirection{narration} She remained there, unmoving ... forever.
	
	\speaker{\textbf{Pod 042}} \shortdirection{narration} It was a completely irrational act.
	
	\speaker{\textbf{Pod 042}} \shortdirection{narration} However, "we" can now understand the reason behind it.
	
	\speaker{\textbf{Pod 042}} \shortdirection{narration} Why it was that 2B didn't move.
	
	\speaker{\textbf{Pod 042}} \shortdirection{narration} Why it was that she didn't speak.
	
	\speaker{\textbf{Pod 042}} \shortdirection{narration} Because "we" are now in that same place, feeling the same thing.
	
	(There is a small pause.)
	
	\speaker{\textbf{Pod 153}} \shortdirection{narration} Everything that lives is designed to end.
	
	\speaker{\textbf{Pod 153}} \shortdirection{narration} "They" are perpetually trapped ...
	
	\speaker{\textbf{Pod 153}} \shortdirection{narration} ... in a never-ending spiral of life and death.
	
	\speaker{\textbf{Pod 153}} \shortdirection{narration} However ... life is all about the struggle within this cycle.
	
	\speaker{\textbf{Pod 153}} \shortdirection{narration} That is what "we" believe. 	
\end{play}